---
title: "SDS Project Regression"
output: html_document
---

```{r global_options, include=FALSE}
# Note the different type of output above?

# The following code is a basic setup of options for your document
knitr::opts_chunk$set(echo = FALSE, # by default: not showing code
                      eval = TRUE, # by default: running code
                      warning = TRUE, # by default: showing warnings
                      message = FALSE, # by default: not showing messages
                      fig.align = "center")

# Load packages
library(tidyverse)
library(plotROC)
library(caret)

```

# 2. **Methods**

*Uploading the packages and data we need from the City of Austin Metro Bike Database and cleaning the dataset.*

```{r echo = FALSE}
#Upload Package
library(tidyverse)
library(readr)
```

```{r}
#Download the data and store it
BikeData <- read_csv("Austin_MetroBike_Trips_20240228.csv")
dim(BikeData)
```

**We start with 35320 rows and 14 columns (variables).**

*Creating our new variables and cleaning the data set:*

```{r}
#Add Seasons
BikeData <- BikeData |> mutate(Season = case_when(
  Month %in% c(12,1,2) ~ "Winter",
  Month %in% c(3,4,5) ~ "Spring",
  Month %in% c(6,7,8) ~ "Summer",
  Month %in% c(9,10,11) ~ "Fall"
)) |>
#Edit the time to take away the colons
  mutate(Time = BikeData$`Checkout Time` |>
  str_remove(":") |>
  str_remove(":")) |>
# Convert Checkout.Date values to days of the week
  mutate(Weekday = ifelse(weekdays(as.Date(`Checkout Date`)) %in% c("Saturday", "Sunday"), "Weekend", "Weekday"))

#Change the var type of time to numerical data}
BikeData$Time <- as.numeric(BikeData$Time)
BikeData$Time <- BikeData$Time %/% 10000 + ((BikeData$Time%%10000)%/%100)/60

#Since we won't be working with every column in this data set, we can create a separate data set to manipulate with only the variables we want to explore.
MetroBike <- BikeData |> select(
  TripId = `Trip ID`, BikeId = `Bicycle ID`,
  Duration = `Trip Duration Minutes`,
  DayType = Weekday, Time, 
  BikeType = `Bike Type`,
  Season, Year) |>
  mutate(BikeType = recode(BikeType, "Classic" = "classic", "Electric" = "electric"))|>
  filter(Year > 2019)

```

```{r echo = TRUE}
#Changing the variables to the correct variable type, and making BikeType a numerical factor for the logistic regression
MetroBike$DayType <- as.character(MetroBike$DayType)
MetroBike$Season <- as.character(MetroBike$Season)
MetroBike$BikeType <- if_else(MetroBike$BikeType == "classic", 0, 1)

dim(MetroBike)
35320
```

# Trip Duration \~ Year + Season with KNN Model

Creating the model, testing with whole dataset:

```{r echo = TRUE}
fit_knn <- knnreg(Duration ~ Year + Time, data = MetroBike, k=5)

MetroBike |> mutate(predicted = predict(fit_knn, MetroBike)) |> select(Duration, predicted) |> head(n=10)

sqrt(mean((MetroBike$Duration - predict(fit_knn, MetroBike))^2))
```

#### **Cross Validation:**

*Creating the folds:*

```{r echo = TRUE}
# Choose number of folds
k = 5 

# To have the same random sample, use set.seed
set.seed(322)

# Randomly order rows in the dataset
data <- MetroBike[sample(nrow(MetroBike)), ] 

# Create k folds from the dataset
folds <- cut(seq(1:nrow(data)), breaks = k, labels = FALSE)
```

*Performing the 5-fold cross validation and finding the mean performance and variatiï¬on:*

```{r}
# Initialize a vector to keep track of the performance for each k-fold
perf_k <- NULL

# Use a for-loop to get performance for each k-fold
for(i in 1:k){
  # Split data into train and test data
  train_not_i <- data[folds != i, ] # train data = all observations except in fold i
  test_i <- data[folds == i, ]  # test data = observations in fold i
  
  # Train model on train data (all but fold i)
  train_model <- knnreg(Duration ~ Year + Time, 
                    data = train_not_i,
                    k=5)
  
  # Performance listed for each test data = fold i
  perf_k[i] <- sqrt(mean((
    test_i$Duration - predict(train_model, newdata = test_i))^2, 
    na.rm = TRUE))
}

# Performance for each fold 
perf_k

#stats
mean(perf_k)
sd(perf_k)
```
